\section{Project Overview}

High-resolution observations of stars orbiting close to our Galaxy's supermassive black hole will enable unique tests of general relativity in the strong gravity regime. Adaptive optics (AO) technology currently provides the sharpest infrared view of the Galactic Center \cite{Ghez_2005}. However, the potential of this technology has not been fully exploited in terms of astrometric and photometric precision due to our incomplete knowledge of the temporal and spatial variations in the point spread function (PSF). In 2011, the Galactic Center Group at UCLA embarked on a project to optimize the extraction of AO astrometry and photometry by incorporating measurements of the Earth's atmospheric turbulence profile and instrumental aberrations to build a model of the PSF spatial variations in every AO image obtained with the NIRC2 instrument on the Keck II telescope. This project, entitled \textbf{AO Optimization} is funded by the W. M. Keck Foundation. The ultimate objective of the AO Optimization project is to apply these methods to past and future observations of stars near the supermassive black hole (SMBH) in order to use their orbits to test General relativity. The star closest to the SMBH (S0-2) will have a periapse passage, between 2016-2020; thus, it is essential that we have AO Optimization tools in place in time for these observations. 

\subsection{Galactic Center Science}

Our project will develop a new methodology that will enable unique tests of Einstein's theory of General Relativity (GR) and black hole growth models. Such tests are within our reach using the telescopes at the W. M. Keck Observatory (WMKO), which have been equipped with Adaptive Optics (AO), a revolutionary technology that has begun to overcome the blurring effects of the Earth's atmosphere that have vexed astronomers for years. Time is of the essence. In order to perform these tests of fundamental physics, we must be able to image with greater precision a rare orbital phase of the star that is the nearest known star to our Galaxy’s supermassive black hole. This star is expected to pass closest to the black hole in 2018, with the effects of GR measurable from observations taken between 2016-2020 if and only if our new methodology is successfully in place by that time.

\subsection{EAC Recommendations}

\subsection{Year 4 Overview}
The following report is written for the External Advisory Committee (EAC) visit in July, 2015. This report contains a status update on the AO Optimization project including completed milestones in Year 4 (2014-07-01 to 2015-07-01) and upcoming milestones for the final Year 5. As a reminder, the AO Optimization project consists of the following high-level goals:
\begin{enumerate}
\item Map NIRC2 instrumental aberrations.
\item Develope algorithms to predict atmospheric-induced aberrations from MASS/DIMM data.
\item Update NIRC2 distortion solution.
\item Upgrade Starfinder 2.0 to extract on-axis PSF from image with spatially varying PSF.
\item Upgrade Starfinder 2.0 to extract stellar astrometry and photometry using varying PSFs.
\item Apply AO Optimization to Galactic Center astrometry.
\item Disseminate AO Optimization to a broader community.
\end{enumerate}




    
    
    
    
    
    
    
  
  
  