\subsection{NIRC2 Hardware Adjustments}
Chromatic elongation on NIRC2 has been a long-term issue, and it is most problematic at $L$-band due to the large bandpass of the filter (KAON 1075). The primary cause of this elongation arises from the dispersion of the infrared dichroic, which was installed improperly with the side of maximum thickness rotated by 180$\deg$ of what it was supposed to be. Additionally, the secondary obscuration was misaligned from the pupil mask. Both issues were fixed by adjusting the two OAPs. The first mirror in the K-mirror was also adjsuted to minimize pupil nutation to get to within 15 pixels (150 mas, 1\% of the pupil), which nearly matches the requirement of 100mm on the primary. Prior to this adjustment, the pupil nutation was a little over 2\%. The figure below shows an example of the $L$-band elongation and the misaligned pupil and secondary obscuration.

Due to these hardware changes, the October 2012 - December 2014 phase diversity grid (hereafter the "old grid") was not valid for the new and usable optical realignment setup. Distortion solution and future Galactic Center data therefore required a new grid. Additionally, the flux of the fiber decreased when we performed tests post-hardware changes (May 2015). As a fix, we had to adjust to the integration times to obtain data with comparable signal-to-noise ratios as the pre-realignment grid. We are currently in the process of taking a new grid of for any post-realignment data.
\subsection{Interpolated Model}
The interpolated model methodology was developed using the "old" grid of phase diversity data. We have two sets of points: "on-grid" points that are spaced $\sim$every 100 pixels in x and y, and "off-grid" points that comprise the rest of the data. These two sets of data are depicted below. The "on-grid" points were used to develop the interpolated model in Zernike space, and the "off-grid" points were modeled and compared to the extracted Zernike coefficients.

A third-order spline in $x$ and $y$ were used in create the model out to 200 Zernike terms. The third-order spline was chosen after modeling with a linear spline and the nearest neighbor; the third-order spline produced results that were more consistent with the extracted Zernike coefficients. 

As shown in the figure below, the off-grid Zernikes were well-modeled with the third-order spline interpolated model, with the exception of some defocus points at some of the positions and some astigmatism. However, overall, the recovery of the Zernike terms by this model is quite good with only about two-thirds of the data. 

A phase-map grid was delivered to the team using the third-order spline interpolated model with all of the old grid data ($\sim$ 150 data points) that is composed of 200 Zernike terms, which is more then sufficient to model a given phasemap based on the power spectrum. This will be used in \textit{StarFinder} 2.0.
    
    
    
  
  